Quantifying maternal reproductive output of chondrichthyan fishes

### 2024-09-24 README.qmd
README

Load sandbar shark maternity data set. Rows are data from individuals sharks.

```{r message=FALSE, warning=FALSE}
library(tidyverse)

@@

*x* is fork length (cm) and *z* is maternal status (0 = non maternal, 1 = maternal).

@@

@@

Bin data into suitable length categories for plotting. Add marginal rug plots to show individual data points.

@@

## 3 Parameter logistic model

Compile the 3 parameter logistic model. The model

@@

```{r}

# Parameter list
pars <- list(m50 = 160, m95 = 170, c = 0.5)

>>>>

Load sandbar shark maternity data set.

```{r message=FALSE, warning=FALSE, include=TRUE}
library(tidyverse)

@@

Rows are data from individuals sharks. *x* is fork length (cm) and *z* is maternal status (0 = non maternal, 1 = maternal).

@@

The dataset consists of maturity and maternity at length data for 1087 female sandbar sharks, 640 of which are mature, and 206 of which were in maternal condition.

@@

Bin data into suitable length categories for plotting, in this case 10cm length bins work well. Marginal rug plots are also helpful for displaying the distribution of individual data points.

@@

## 3 parameter logistic maternity function (3PLF)

To run the 3PLF model, load the `TMB` library, compile the `C++` file and load the compiled file.

@@

Initialize a list of parameters for the model with their starting values, then construct the objective function to be minimised using R.

```{r}
# Parameter list
pars <- list(m50 = 160, m95 = 170, c = 0.5)
